---
title: "Topic Modeling for 'Good Taste' and 'Bad Taste' Definitions"
format: html
---

::: {.callout-note}
This report was generated using AI under general human direction. At the time of generation, the contents have not been comprehensively reviewed by a human analyst.
:::

# Introduction

This report uses **BERTopic** to extract topics from open-ended survey responses defining what constitutes "Good Taste" and "Bad Taste". The BERTopic models were trained in Python and the results saved to disk. We visualize the distributions of topics below using the `tidyverse` and `ggplot2`.

# Setup and data loading

We load the necessary R packages and load our summarized topic data.

```{r}
#| label: load-packages
library(dplyr)
library(ggplot2)
library(readr)
library(stringr)
library(jsonlite)
library(tidyr)
library(tidytext)
```

# Topic modeling results

The short texts defining "Good Taste" and "Bad Taste" were clustered into 5 broad themes each using BERTopic. We load the summarized results from those models.

```{r}
#| label: load-models
# Load the pre-computed topic info tables
good_topic_info <- read_csv("Tabs/good_topic_info.csv", show_col_types = FALSE)
bad_topic_info <- read_csv("Tabs/bad_topic_info.csv", show_col_types = FALSE)

# Clean up the Python list formatting in the Representation column
clean_keywords <- function(rep_str) {
  str_remove_all(rep_str, "\\[|\\]|'")
}
good_topic_info$Keywords <- sapply(good_topic_info$Representation, clean_keywords)
bad_topic_info$Keywords <- sapply(bad_topic_info$Representation, clean_keywords)

# Remove the messy Representation and NaN Representative_Docs columns for the table
good_topic_table <- good_topic_info %>% select(Topic, Count, Name, Keywords)
bad_topic_table <- bad_topic_info %>% select(Topic, Count, Name, Keywords)

# Ensure Tabs directory exists and save the tables as HTML
dir.create("Tabs", showWarnings = FALSE)

# Write out simple HTML tables
writeLines(
  knitr::kable(good_topic_table, format = "html"), 
  "Tabs/good_taste_summary_table.html"
)
writeLines(
  knitr::kable(bad_topic_table, format = "html"), 
  "Tabs/bad_taste_summary_table.html"
)

head(good_topic_info, 10)
head(bad_topic_info, 10)
```

# Visualizing topic distributions

We use `ggplot2` to visualize the distribution and prominence of each theme.

*(Note: Topic `-1` in BERTopic refers to outliers that could not be confidently assigned to a cluster. We exclude it from the visualizations below.)*

```{r}
#| label: visualize-topics
#| fig-width: 8
#| fig-height: 6

# Ensure Plots directory exists
dir.create("Plots", showWarnings = FALSE)

# Good Taste Topic Frequencies
p_good <- ggplot(good_topic_info %>% filter(Topic != -1), aes(x = reorder(Name, Count), y = Count)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  coord_flip() +
  theme_minimal(base_size = 14) +
  labs(
    title = "Good Taste: Topic Frequencies", 
    x = "Topic Name (Top Words)", 
    y = "Number of Responses"
  )

print(p_good)
ggsave("Plots/good_taste_topics.png", plot = p_good, width = 8, height = 6)

# Bad Taste Topic Frequencies
p_bad <- ggplot(bad_topic_info %>% filter(Topic != -1), aes(x = reorder(Name, Count), y = Count)) +
  geom_bar(stat = "identity", fill = "indianred") +
  coord_flip() +
  theme_minimal(base_size = 14) +
  labs(
    title = "Bad Taste: Topic Frequencies", 
    x = "Topic Name (Top Words)", 
    y = "Number of Responses"
  )

print(p_bad)
ggsave("Plots/bad_taste_topics.png", plot = p_bad, width = 8, height = 6)
```

# Keyword Importance (c-TF-IDF)

To better understand *why* each topic was formed, we can look at the mathematical importance (c-TF-IDF score) of the top keywords for each topic. We extract these weights directly from the saved model metadata.

### Interpretation

* **Good Taste** themes seem heavily divided between definitions relying on external consensus or high-art aesthetics (Topic 0: *art, appreciate, pleasing*) versus definitions emphasizing alignment with personal preferences (Topic 1: *say, like, person*). 
* **Bad Taste** themes include lack of independence or "following the crowd" (Topic 0), enjoying "loud" or "gaudy" things (Topic 1, Topic 2), or specifically enjoying "low-brow" mass media (Topic 5: *music, reality tv, rap, movies*).

```{r}
#| label: visualize-keywords
#| fig-width: 10
#| fig-height: 8

# Function to parse the topics.json file into a ggplot-friendly dataframe
extract_keyword_weights <- function(json_path) {
  # Read from root path because the Quarto file runs from the report/ dir
  # but the string provided was relative to root in my tests.
  topics_data <- fromJSON(json_path)$topic_representations
  
  # Remove the outlier topic "-1"
  topics_data[["-1"]] <- NULL
  
  # Convert nested list into a dataframe
  df_list <- lapply(names(topics_data), function(topic_id) {
    # Each item is a matrix/array where [,1] is the word and [,2] is the score
    mat <- topics_data[[topic_id]]
    data.frame(
      Topic = paste("Topic", topic_id),
      Word = as.character(mat[,1]),
      Score = as.numeric(mat[,2]),
      stringsAsFactors = FALSE
    )
  })
  
  do.call(rbind, df_list)
}

# Extract for Good Taste
good_weights <- extract_keyword_weights("../good_taste_model/topics.json")

# Plot Good Taste Keywords
p_good_keys <- good_weights %>%
  group_by(Topic) %>%
  top_n(8, Score) %>% # Get top 8 words per topic
  ungroup() %>%
  mutate(Word = reorder_within(Word, Score, Topic)) %>%
  ggplot(aes(x = Word, y = Score, fill = Topic)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ Topic, scales = "free_y") +
  coord_flip() +
  scale_x_reordered() +
  theme_minimal() +
  labs(
    title = "Good Taste: Keyword Importance by Topic",
    x = NULL, y = "c-TF-IDF Score"
  )

print(p_good_keys)
ggsave("Plots/good_taste_keywords.png", plot = p_good_keys, width = 10, height = 8)

# Extract for Bad Taste
bad_weights <- extract_keyword_weights("../bad_taste_model/topics.json")

# Plot Bad Taste Keywords
p_bad_keys <- bad_weights %>%
  group_by(Topic) %>%
  top_n(8, Score) %>%
  ungroup() %>%
  mutate(Word = reorder_within(Word, Score, Topic)) %>%
  ggplot(aes(x = Word, y = Score, fill = Topic)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ Topic, scales = "free_y") +
  coord_flip() +
  scale_x_reordered() +
  theme_minimal() +
  labs(
    title = "Bad Taste: Keyword Importance by Topic",
    x = NULL, y = "c-TF-IDF Score"
  )

print(p_bad_keys)
ggsave("Plots/bad_taste_keywords.png", plot = p_bad_keys, width = 10, height = 8)
```

# Example Responses (Pseudo-Representative Documents)

Because the heavy mathematical models only saved the keyword weights to disk, we can use R to find the best example responses for each topic. We do this by scanning the original survey text and finding the quotes that contain the highest number of a topic's core keywords.

```{r}
#| label: extract-examples
#| results: asis

# Load the original survey text
raw_data <- read_csv("../data/FolkTaste_CleanData.csv", show_col_types = FALSE)
valid_data <- raw_data %>% filter(Taste_Possibility == 'YES')

good_docs <- valid_data$GoodTaste_Def[!is.na(valid_data$GoodTaste_Def)]
bad_docs <- valid_data$BadTaste_Def[!is.na(valid_data$BadTaste_Def)]

# Function to score documents based on keyword matching and return the top 2
find_examples <- function(docs, keywords_str, n = 2) {
  # Split the comma-separated keywords
  keys <- str_split(keywords_str, ",\\s*")[[1]]
  
  # Score each document by counting keyword occurrences
  scores <- sapply(docs, function(d) {
    if (is.na(d) || nchar(trimws(d)) < 10) return(-1) # Penalize empty/very short responses
    d_lower <- tolower(d)
    sum(sapply(keys, function(k) str_detect(d_lower, fixed(k))))
  })
  
  # Get indices of the top scoring documents
  top_idx <- order(scores, decreasing = TRUE)[1:n]
  
  # Format as a nice HTML bulleted list
  paste(paste0("&bull; <em>\"", docs[top_idx], "\"</em>"), collapse = "<br><br>")
}

# Apply to Good Taste
good_topic_table$Example_Responses <- sapply(good_topic_table$Keywords, function(kw) {
  find_examples(good_docs, kw, n = 2)
})

# Apply to Bad Taste
bad_topic_table$Example_Responses <- sapply(bad_topic_table$Keywords, function(kw) {
  find_examples(bad_docs, kw, n = 2)
})

# Save the updated tables to the Tabs directory
writeLines(
  knitr::kable(good_topic_table, format = "html", escape = FALSE), 
  "Tabs/good_taste_examples_table.html"
)
writeLines(
  knitr::kable(bad_topic_table, format = "html", escape = FALSE), 
  "Tabs/bad_taste_examples_table.html"
)
```

### Good Taste Examples
```{r}
#| echo: false
#| results: asis
knitr::kable(good_topic_table %>% select(Topic, Name, Example_Responses), format = "html", escape = FALSE)
```

### Bad Taste Examples
```{r}
#| echo: false
#| results: asis
knitr::kable(bad_topic_table %>% select(Topic, Name, Example_Responses), format = "html", escape = FALSE)
```
