---
title: "Topic Modeling for 'Good Taste' and 'Bad Taste' Definitions"
format: html
---

::: {.callout-note}
This report was generated using AI under general human direction. At the time of generation, the contents have not been comprehensively reviewed by a human analyst.
:::

# Introduction

This report uses **BERTopic** to extract topics from open-ended survey responses defining what constitutes "Good Taste" and "Bad Taste". The BERTopic models were trained in Python and the results saved to disk. We visualize the distributions of topics below using the `tidyverse` and `ggplot2`.

# Setup and data loading

We load the necessary R packages and load our summarized topic data.

```{r}
#| label: load-packages
library(dplyr)
library(ggplot2)
library(readr)
library(stringr)
```

# Topic modeling results

The short texts defining "Good Taste" and "Bad Taste" were clustered into 5 broad themes each using BERTopic. We load the summarized results from those models.

```{r}
#| label: load-models
# Load the pre-computed topic info tables
good_topic_info <- read_csv("Tabs/good_topic_info.csv", show_col_types = FALSE)
bad_topic_info <- read_csv("Tabs/bad_topic_info.csv", show_col_types = FALSE)

# Clean up the Python list formatting in the Representation column
clean_keywords <- function(rep_str) {
  str_remove_all(rep_str, "\\[|\\]|'")
}
good_topic_info$Keywords <- sapply(good_topic_info$Representation, clean_keywords)
bad_topic_info$Keywords <- sapply(bad_topic_info$Representation, clean_keywords)

# Remove the messy Representation and NaN Representative_Docs columns for the table
good_topic_table <- good_topic_info %>% select(Topic, Count, Name, Keywords)
bad_topic_table <- bad_topic_info %>% select(Topic, Count, Name, Keywords)

# Ensure Tabs directory exists and save the tables as HTML
dir.create("Tabs", showWarnings = FALSE)

# Write out simple HTML tables
writeLines(
  knitr::kable(good_topic_table, format = "html"), 
  "Tabs/good_taste_summary_table.html"
)
writeLines(
  knitr::kable(bad_topic_table, format = "html"), 
  "Tabs/bad_taste_summary_table.html"
)

head(good_topic_info, 10)
head(bad_topic_info, 10)
```

# Visualizing topic distributions

We use `ggplot2` to visualize the distribution and prominence of each theme.

*(Note: Topic `-1` in BERTopic refers to outliers that could not be confidently assigned to a cluster. We exclude it from the visualizations below.)*

```{r}
#| label: visualize-topics
#| fig-width: 8
#| fig-height: 6

# Ensure Plots directory exists
dir.create("Plots", showWarnings = FALSE)

# Good Taste Topic Frequencies
p_good <- ggplot(good_topic_info %>% filter(Topic != -1), aes(x = reorder(Name, Count), y = Count)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  coord_flip() +
  theme_minimal(base_size = 14) +
  labs(
    title = "Good Taste: Topic Frequencies", 
    x = "Topic Name (Top Words)", 
    y = "Number of Responses"
  )

print(p_good)
ggsave("Plots/good_taste_topics.png", plot = p_good, width = 8, height = 6)

# Bad Taste Topic Frequencies
p_bad <- ggplot(bad_topic_info %>% filter(Topic != -1), aes(x = reorder(Name, Count), y = Count)) +
  geom_bar(stat = "identity", fill = "indianred") +
  coord_flip() +
  theme_minimal(base_size = 14) +
  labs(
    title = "Bad Taste: Topic Frequencies", 
    x = "Topic Name (Top Words)", 
    y = "Number of Responses"
  )

print(p_bad)
ggsave("Plots/bad_taste_topics.png", plot = p_bad, width = 8, height = 6)
```
