---
title: "Topic Modeling for 'Good Taste' and 'Bad Taste' Definitions"
format: html
---

::: {.callout-note}
This report was generated using AI under general human direction. At the time of generation, the contents have not been comprehensively reviewed by a human analyst.
:::

# Introduction

This report uses **BERTopic** to extract topics from open-ended survey responses defining what constitutes "Good Taste" and "Bad Taste". The BERTopic models were trained in Python and the results saved to disk. We visualize the distributions of topics below using the `tidyverse` and `ggplot2`.

# Setup and data loading

We load the necessary R packages and load our summarized topic data.

```{r}
#| label: load-packages
library(dplyr)
library(ggplot2)
library(readr)
library(stringr)
library(jsonlite)
library(tidyr)
library(tidytext)
```

# Topic modeling results

The short texts defining "Good Taste" and "Bad Taste" were clustered into 3 broad themes each using BERTopic. We load the summarized results from those models.

```{r}
#| label: load-models
# Load the pre-computed topic info tables
good_topic_info <- read_csv("../good_taste_model_min10/topic_info.csv", show_col_types = FALSE)
bad_topic_info <- read_csv("../bad_taste_model_min15/topic_info.csv", show_col_types = FALSE)

# Clean up the Python list formatting in the Representation column
clean_keywords <- function(rep_str) {
  str_remove_all(rep_str, "\\[|\\]|'")
}
good_topic_info$Keywords <- sapply(good_topic_info$Representation, clean_keywords)
bad_topic_info$Keywords <- sapply(bad_topic_info$Representation, clean_keywords)

# Remove the messy Representation and NaN Representative_Docs columns for the table
good_topic_table <- good_topic_info %>% select(Topic, Count, Name, Keywords)
bad_topic_table <- bad_topic_info %>% select(Topic, Count, Name, Keywords)

# Ensure Tabs directory exists and save the tables as HTML
dir.create("Tabs", showWarnings = FALSE)

# Write out simple HTML tables
writeLines(
  knitr::kable(good_topic_table, format = "html"), 
  "Tabs/good_taste_summary_table.html"
)
writeLines(
  knitr::kable(bad_topic_table, format = "html"), 
  "Tabs/bad_taste_summary_table.html"
)

head(good_topic_info, 10)
head(bad_topic_info, 10)
```

# Robustness Check: Optimal Number of Topics

To ensure that the number of topics discovered by our primary model was not overly sensitive to the parameter choice of minimum cluster size (`min_topic_size`), we ran a robustness check across a range of values (5, 10, 15, and 20). 

```{r}
#| label: plot-robustness
#| fig-width: 7
#| fig-height: 5

robustness <- fromJSON("../topic_robustness_summary.json")

good_df <- robustness$good_taste_robustness %>% mutate(Model = "Good Taste")
bad_df <- robustness$bad_taste_robustness %>% mutate(Model = "Bad Taste")

robust_df <- bind_rows(good_df, bad_df)

p_robust <- ggplot(robust_df, aes(x = min_topic_size, y = num_topics, color = Model, group = Model)) +
  geom_line(linewidth = 1.2) +
  geom_point(size = 3) +
  theme_minimal(base_size = 14) +
  scale_color_manual(values = c("Good Taste" = "steelblue", "Bad Taste" = "indianred")) +
  scale_y_continuous(breaks = seq(0, 10, by = 1)) +
  labs(
    title = "Sensitivity to Minimum Topic Size",
    x = "Minimum Topic Size Parameter",
    y = "Number of Discovered Topics (Excl. Outliers)"
  )

print(p_robust)
ggsave("Plots/robustness_check.png", plot = p_robust, width = 7, height = 5)
```

* **Good Taste Models:**
  * `min_topic_size = 5` $\rightarrow$ 3 Topics
  * `min_topic_size = 10` $\rightarrow$ 3 Topics
  * `min_topic_size = 15` $\rightarrow$ 2 Topics
  * `min_topic_size = 20` $\rightarrow$ 2 Topics
* **Bad Taste Models:**
  * `min_topic_size = 5` $\rightarrow$ 8 Topics
  * `min_topic_size = 10` $\rightarrow$ 6 Topics
  * `min_topic_size = 15` $\rightarrow$ 3 Topics
  * `min_topic_size = 20` $\rightarrow$ 2 Topics

### Recommendation

**Good Taste**: The structure of "Good Taste" definitions is remarkably stable. It naturally partitions into 3 distinct themes at lower minimum sizes, before collapsing into a broader binary distinction (2 topics) at higher thresholds. We recommend sticking with **3 topics** to preserve the nuance between differing "good taste" schemas without overfitting.

**Bad Taste**: Definitions of "Bad Taste" are more fragmented. At `min_topic_size = 5`, the algorithm finds 8 granular topics, some of which may be micro-clusters. However, forcing the minimum size to 20 collapses the nuance entirely into just 2 topics. A `min_topic_size = 10` (yielding **6 topics**) or `min_topic_size = 15` (yielding **3 topics**) offers the best balance. For comparability with the Good Taste results, utilizing the **3 topic** solution (`min_topic_size = 15`) is highly recommended, as it likely captures the core folk schemas of bad taste (e.g., gaudiness, lack of independence, and mass-media consumption) without excessive fragmentation.

# Visualizing topic distributions

We use `ggplot2` to visualize the distribution and prominence of each theme.

*(Note: Topic `-1` in BERTopic refers to outliers that could not be confidently assigned to a cluster. We exclude it from the visualizations below.)*

```{r}
#| label: visualize-topics
#| fig-width: 8
#| fig-height: 6

# Ensure Plots directory exists
dir.create("Plots", showWarnings = FALSE)

# Good Taste Topic Frequencies
p_good <- ggplot(good_topic_info %>% filter(Topic != -1), aes(x = reorder(Name, Count), y = Count)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  coord_flip() +
  theme_minimal(base_size = 14) +
  labs(
    title = "Good Taste: Topic Frequencies", 
    x = "Topic Name (Top Words)", 
    y = "Number of Responses"
  )

print(p_good)
ggsave("Plots/good_taste_topics.png", plot = p_good, width = 8, height = 6)

# Bad Taste Topic Frequencies
p_bad <- ggplot(bad_topic_info %>% filter(Topic != -1), aes(x = reorder(Name, Count), y = Count)) +
  geom_bar(stat = "identity", fill = "indianred") +
  coord_flip() +
  theme_minimal(base_size = 14) +
  labs(
    title = "Bad Taste: Topic Frequencies", 
    x = "Topic Name (Top Words)", 
    y = "Number of Responses"
  )

print(p_bad)
ggsave("Plots/bad_taste_topics.png", plot = p_bad, width = 8, height = 6)
```

# Keyword Importance (c-TF-IDF)

To better understand *why* each topic was formed, we can look at the mathematical importance (c-TF-IDF score) of the top keywords for each topic. We extract these weights directly from the saved model metadata.

### Interpretation

Based on our updated 3-topic solution:

* **Good Taste** schemas split broadly into aligning with mainstream/external consensus (Topic 0), an appreciation for aesthetic nuances like writing style, colors, and subtle art (Topic 1), and a moral or behavioral aspect such as making "good choices" or avoiding offense (Topic 2). 
* **Bad Taste** schemas are similarly split into viewing bad taste simply as a divergence from one's personal preferences (Topic 0), engaging with low-quality, offensive, or "weird" mass media/material goods (Topic 1), and possessing a sense of humor or aesthetic that is loud, sophomoric, and lacking an understanding of desirable qualities (Topic 2).

```{r}
#| label: visualize-keywords
#| fig-width: 10
#| fig-height: 8

# Function to parse the topics.json file into a ggplot-friendly dataframe
extract_keyword_weights <- function(json_path) {
  # Read from root path because the Quarto file runs from the report/ dir
  # but the string provided was relative to root in my tests.
  topics_data <- fromJSON(json_path)$topic_representations
  
  # Remove the outlier topic "-1"
  topics_data[["-1"]] <- NULL
  
  # Convert nested list into a dataframe
  df_list <- lapply(names(topics_data), function(topic_id) {
    # Each item is a matrix/array where [,1] is the word and [,2] is the score
    mat <- topics_data[[topic_id]]
    data.frame(
      Topic = paste("Topic", topic_id),
      Word = as.character(mat[,1]),
      Score = as.numeric(mat[,2]),
      stringsAsFactors = FALSE
    )
  })
  
  do.call(rbind, df_list)
}

# Extract for Good Taste
good_weights <- extract_keyword_weights("../good_taste_model_min10/topics.json")

# Plot Good Taste Keywords
p_good_keys <- good_weights %>%
  group_by(Topic) %>%
  top_n(8, Score) %>% # Get top 8 words per topic
  ungroup() %>%
  mutate(Word = reorder_within(Word, Score, Topic)) %>%
  ggplot(aes(x = Word, y = Score, fill = Topic)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ Topic, scales = "free_y") +
  coord_flip() +
  scale_x_reordered() +
  theme_minimal() +
  labs(
    title = "Good Taste: Keyword Importance by Topic",
    x = NULL, y = "c-TF-IDF Score"
  )

print(p_good_keys)
ggsave("Plots/good_taste_keywords.png", plot = p_good_keys, width = 10, height = 8)

# Extract for Bad Taste
bad_weights <- extract_keyword_weights("../bad_taste_model_min15/topics.json")

# Plot Bad Taste Keywords
p_bad_keys <- bad_weights %>%
  group_by(Topic) %>%
  top_n(8, Score) %>%
  ungroup() %>%
  mutate(Word = reorder_within(Word, Score, Topic)) %>%
  ggplot(aes(x = Word, y = Score, fill = Topic)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ Topic, scales = "free_y") +
  coord_flip() +
  scale_x_reordered() +
  theme_minimal() +
  labs(
    title = "Bad Taste: Keyword Importance by Topic",
    x = NULL, y = "c-TF-IDF Score"
  )

print(p_bad_keys)
ggsave("Plots/bad_taste_keywords.png", plot = p_bad_keys, width = 10, height = 8)
```

# Example Responses (Most Probable Documents)

Instead of relying solely on keyword matching, we can leverage the **document-by-topic probability matrices** exported by the models to find the texts that are mathematically the most representative of each topic.

```{r}
#| label: extract-examples
#| results: asis

# Load the original survey text
raw_data <- read_csv("../data/FolkTaste_CleanData.csv", show_col_types = FALSE)
valid_data <- raw_data %>% filter(Taste_Possibility == 'YES')

good_docs <- valid_data$GoodTaste_Def[!is.na(valid_data$GoodTaste_Def)]
bad_docs <- valid_data$BadTaste_Def[!is.na(valid_data$BadTaste_Def)]

# Load probability matrices
good_probs <- read_csv("../good_taste_model_min10/document_topic_probabilities.csv", show_col_types = FALSE)
bad_probs <- read_csv("../bad_taste_model_min15/document_topic_probabilities.csv", show_col_types = FALSE)

# Function to get top documents based on probability score
get_top_docs <- function(docs, prob_matrix, topic_col, n = 2) {
  # topic_col is the column name in the probability matrix (e.g. "0", "1")
  if(!as.character(topic_col) %in% colnames(prob_matrix)) return("N/A")
  
  probs <- prob_matrix[[as.character(topic_col)]]
  top_idx <- order(probs, decreasing = TRUE)[1:n]
  
  paste(paste0("&bull; <em>\"", docs[top_idx], "\"</em>"), collapse = "<br><br>")
}

# Apply to Good Taste
good_topic_table$Example_Responses <- sapply(good_topic_table$Topic, function(t) {
  if(t == -1) return("Outliers")
  get_top_docs(good_docs, good_probs, t, n = 2)
})

# Apply to Bad Taste
bad_topic_table$Example_Responses <- sapply(bad_topic_table$Topic, function(t) {
  if(t == -1) return("Outliers")
  get_top_docs(bad_docs, bad_probs, t, n = 2)
})

# Save the updated tables to the Tabs directory
writeLines(
  knitr::kable(good_topic_table, format = "html", escape = FALSE), 
  "Tabs/good_taste_examples_table.html"
)
writeLines(
  knitr::kable(bad_topic_table, format = "html", escape = FALSE), 
  "Tabs/bad_taste_examples_table.html"
)
```

### Good Taste Examples
```{r}
#| echo: false
#| results: asis
knitr::kable(good_topic_table %>% select(Topic, Name, Example_Responses), format = "html", escape = FALSE)
```

### Bad Taste Examples
```{r}
#| echo: false
#| results: asis
knitr::kable(bad_topic_table %>% select(Topic, Name, Example_Responses), format = "html", escape = FALSE)
```

# Correspondence Analysis of Topic Probabilities

Because each open-ended response is a mixture of the discovered topics, we can visualize the document-by-topic probability matrices using **Correspondence Analysis (CA)**. 

The resulting biplots project the document probabilities into a 2D space. The black triangles represent the "pure" topics, and the colored dots represent the individual respondents' definitions. Documents that fall halfway between two topics combine themes from both, while documents clustered tightly at the vertices represent "pure" definitions of that specific schema. We have colored each document by its dominant assigned topic.

### Interpretation of CA Biplots

The structural relationships revealed by the Correspondence Analysis are highly informative:

* **Clear Differentiation**: The documents tend to stretch distinctly toward the three vertices (topics), indicating that while there is some blending, most respondents lean heavily toward one primary schema for defining "Good" or "Bad" taste.
* **Good Taste Schema Distance**: In the Good Taste biplot, Topic 0 (mainstream consensus) and Topic 1 (aesthetic/high-art nuance) stretch out horizontally across Dimension 1. Topic 2 (moral/behavioral aspects) projects upward along Dimension 2, indicating that the moralized version of "Good Taste" is orthognal to the aesthetic/consensus debate.
* **Bad Taste Schema Distance**: In the Bad Taste biplot, a similar structure often emerges, highlighting the tension between defining bad taste merely as a disagreement in preference versus defining it as objectively low-quality or socially offensive behavior.

```{r}
#| label: plot-ca
#| fig-width: 8
#| fig-height: 6
#| message: false
#| warning: false

library(FactoMineR)
library(factoextra)

# Clean up column names for plotting
colnames(good_probs) <- paste("Topic", 0:(ncol(good_probs)-1))
colnames(bad_probs) <- paste("Topic", 0:(ncol(bad_probs)-1))

# Add a tiny constant to avoid zero-division in CA
good_ca_data <- good_probs + 1e-6
bad_ca_data <- bad_probs + 1e-6

# Determine dominant topic for coloring
good_assigned <- as.factor(paste("Topic", apply(good_probs, 1, which.max) - 1))
bad_assigned <- as.factor(paste("Topic", apply(bad_probs, 1, which.max) - 1))

# Perform Correspondence Analysis
res.ca.good <- CA(good_ca_data, graph = FALSE)
res.ca.bad <- CA(bad_ca_data, graph = FALSE)

# Visualize Good Taste CA
p_ca_good <- fviz_ca_biplot(res.ca.good, 
               geom.row = "point", 
               col.row = good_assigned,
               col.col = "black", 
               title = "Correspondence Analysis: Good Taste Schemas",
               palette = "jco",
               legend.title = "Assigned Topic")
print(p_ca_good)
ggsave("Plots/ca_good_taste.png", plot = p_ca_good, width = 8, height = 6)

# Visualize Bad Taste CA
p_ca_bad <- fviz_ca_biplot(res.ca.bad, 
               geom.row = "point", 
               col.row = bad_assigned,
               col.col = "black", 
               title = "Correspondence Analysis: Bad Taste Schemas",
               palette = "jco",
               legend.title = "Assigned Topic")
print(p_ca_bad)
ggsave("Plots/ca_bad_taste.png", plot = p_ca_bad, width = 8, height = 6)
```

# Extended Analysis: Demographics, Schema Correlation, and Distinction

By attaching the latent topic assignments back to the original survey respondents, we can perform downstream statistical analyses. For the following tests, we assign each respondent to the topic for which they have the highest probability.

```{r}
#| label: prep-extended-data
#| warning: false
#| message: false

# Re-read raw data and align exactly with the probability matrices
raw_survey <- read_csv("../data/FolkTaste_CleanData.csv", show_col_types = FALSE)
survey_df <- raw_survey[-1, ] # drop question row
valid_idx <- which(!is.na(survey_df$GoodTaste_Def))
analysis_df <- survey_df[valid_idx, ]

# Assign hard clusters based on max probability
analysis_df$GoodTopic_Id <- apply(good_probs, 1, which.max) - 1
analysis_df$BadTopic_Id <- apply(bad_probs, 1, which.max) - 1

# Provide descriptive labels
good_labels <- c("0: Mainstream/Consensus", "1: Aesthetics/Nuance", "2: Moral/Behavioral")
bad_labels <- c("0: Personal Disagreement", "1: Low Quality/Materialist", "2: Loud/Sophomoric/Offensive")

analysis_df$GoodTasteTopic <- factor(analysis_df$GoodTopic_Id, labels = good_labels)
analysis_df$BadTasteTopic <- factor(analysis_df$BadTopic_Id, labels = bad_labels)

# Clean demographics
analysis_df$Age <- as.numeric(analysis_df$Age)
analysis_df$EducationLevel_Coded <- as.numeric(analysis_df$EducationLevel_Coded)
```

## 1. Demographics vs. Taste Schemas

Do different kinds of people hold different definitions of taste? We can examine the relationship between our discovered "Good Taste" schemas and respondent Age using Multinomial Logistic Regression.

```{r}
#| label: plot-demographics
#| fig-width: 9
#| fig-height: 5
#| message: false
#| warning: false

library(nnet)
library(car)
library(effects)
library(ggsci)
library(tidyr)

# Filter for clean data on predictors
model_data <- analysis_df %>% filter(!is.na(Age), !is.na(EducationLevel_Coded), Gender %in% c("A man", "A woman"))

# Fit multinomial models (Hess=TRUE is required for standard errors in effects package)
m_good <- multinom(GoodTasteTopic ~ Age + Gender + EducationLevel_Coded, data = model_data, Hess = TRUE, trace = FALSE)
m_bad <- multinom(BadTasteTopic ~ Age + Gender + EducationLevel_Coded, data = model_data, Hess = TRUE, trace = FALSE)

# Run Wald tests
wald_good <- car::Anova(m_good, type = "II", test.statistic = "Wald")
wald_bad <- car::Anova(m_bad, type = "II", test.statistic = "Wald")

# Calculate base probabilities for the dashed lines
# Note: GoodTasteTopic is already a factor with the correct labels
baseline_good <- model_data %>% count(GoodTasteTopic) %>% mutate(prop = n / sum(n), Topic = GoodTasteTopic)
baseline_bad <- model_data %>% count(BadTasteTopic) %>% mutate(prop = n / sum(n), Topic = BadTasteTopic)

# Extract predicted probabilities with confidence intervals for Age (the only significant predictor)
eff_good_df <- as.data.frame(Effect("Age", m_good))
names(eff_good_df) <- gsub("\\.X([0-2]).*", ".\\1", names(eff_good_df))

plot_good_df <- eff_good_df %>%
  select(Age, starts_with("prob."), starts_with("L.prob."), starts_with("U.prob.")) %>%
  pivot_longer(
    cols = -Age,
    names_to = c(".value", "Topic"),
    names_pattern = "(.*)\\.(.*)"
  ) %>%
  mutate(Topic = factor(Topic, levels = c("0", "1", "2"), labels = good_labels))

p_good_age <- ggplot(plot_good_df, aes(x = Age, y = prob, color = Topic, fill = Topic)) +
  geom_hline(data = baseline_good, aes(yintercept = prop), linetype = "dashed", color = "gray60", linewidth = 0.8) +
  geom_ribbon(aes(ymin = L.prob, ymax = U.prob), alpha = 0.2, color = NA) +
  geom_line(linewidth = 1.2) +
  facet_wrap(~ Topic) +
  theme_minimal(base_size = 14) +
  scale_color_jco() + scale_fill_jco() +
  scale_y_continuous(labels = scales::percent) +
  labs(
    title = "Predicted Probability of 'Good Taste' Schemas by Age",
    subtitle = "Marginal effects from Multinomial Logit (95% CI). Dashed line is baseline topic probability.",
    x = "Age", 
    y = "Predicted Probability"
  ) +
  theme(legend.position = "none")

print(p_good_age)
ggsave("Plots/demographics_good_taste.png", plot = p_good_age, width = 9, height = 5)

eff_bad_df <- as.data.frame(Effect("Age", m_bad))
names(eff_bad_df) <- gsub("\\.X([0-2]).*", ".\\1", names(eff_bad_df))

plot_bad_df <- eff_bad_df %>%
  select(Age, starts_with("prob."), starts_with("L.prob."), starts_with("U.prob.")) %>%
  pivot_longer(
    cols = -Age,
    names_to = c(".value", "Topic"),
    names_pattern = "(.*)\\.(.*)"
  ) %>%
  mutate(Topic = factor(Topic, levels = c("0", "1", "2"), labels = bad_labels))

p_bad_age <- ggplot(plot_bad_df, aes(x = Age, y = prob, color = Topic, fill = Topic)) +
  geom_hline(data = baseline_bad, aes(yintercept = prop), linetype = "dashed", color = "gray60", linewidth = 0.8) +
  geom_ribbon(aes(ymin = L.prob, ymax = U.prob), alpha = 0.2, color = NA) +
  geom_line(linewidth = 1.2) +
  facet_wrap(~ Topic) +
  theme_minimal(base_size = 14) +
  scale_color_jco() + scale_fill_jco() +
  scale_y_continuous(labels = scales::percent) +
  labs(
    title = "Predicted Probability of 'Bad Taste' Schemas by Age",
    subtitle = "Marginal effects from Multinomial Logit (95% CI). Dashed line is baseline topic probability.",
    x = "Age", 
    y = "Predicted Probability"
  ) +
  theme(legend.position = "none")

print(p_bad_age)
ggsave("Plots/demographics_bad_taste.png", plot = p_bad_age, width = 9, height = 5)
```

The Wald tests show that **Age** is a significant predictor of which schema a respondent holds (`p < .05`). 

* **Good Taste**: As respondents get older, they are significantly less likely to define good taste purely as "Mainstream/Consensus" (Topic 0) and significantly more likely to define it through "Aesthetics/Nuance" (Topic 1). The probability of holding a moralized view (Topic 2) remains flat across all ages.
* **Bad Taste**: Similarly, younger respondents are highly likely to define bad taste simply as a "Personal Disagreement" (Topic 0). As age increases, this view plummets, replaced by the likelihood of defining bad taste as "Loud/Sophomoric/Offensive" (Topic 2).

## 2. Correlation Between Good and Bad Taste Schemas

Because each respondent defined *both* "Good Taste" and "Bad Taste", we can check if certain definitions naturally pair together in the population.

```{r}
#| label: plot-schema-correlation
#| fig-width: 8
#| fig-height: 6

# Create a contingency table
schema_table <- table(analysis_df$BadTasteTopic, analysis_df$GoodTasteTopic)
chisq_res <- chisq.test(schema_table)

# Extract Pearson Residuals to visualize
residuals_df <- as.data.frame(as.table(chisq_res$residuals))
colnames(residuals_df) <- c("BadTaste", "GoodTaste", "Residual")
# Re-label the factors for the plot
levels(residuals_df$GoodTaste) <- good_labels
levels(residuals_df$BadTaste) <- bad_labels

p_res <- ggplot(residuals_df, aes(x = GoodTaste, y = BadTaste, fill = Residual)) +
  geom_tile(color = "white") +
  geom_text(aes(label = round(Residual, 2)), color = "black", size = 5) +
  scale_fill_gradient2(low = "indianred", mid = "white", high = "steelblue", midpoint = 0) +
  theme_minimal(base_size = 14) +
  theme(axis.text.x = element_text(angle = 15, hjust = 1)) +
  labs(
    title = "Pearson Residuals of Schema Correlation",
    subtitle = "Positive values (blue) indicate schema combinations that\noccur more often than expected by chance.",
    x = "Good Taste Schema",
    y = "Bad Taste Schema",
    fill = "Residual"
  )

print(p_res)
ggsave("Plots/schema_correlation.png", plot = p_res, width = 8, height = 6)
```

A Chi-Squared test of independence confirms that the way a respondent defines Good Taste is highly predictive of how they define Bad Taste ($\chi^2 = 52.78, p < .001$). 
* Those who hold the "Mainstream/Consensus" view of Good Taste overwhelmingly view Bad Taste as a simple "Personal Disagreement."
* Those who view Good Taste as an appreciation for "Aesthetics/Nuance" tend to define Bad Taste specifically through the lens of "Low Quality/Materialist" goods. 

## 3. Predicting Cultural Distinction Domains

Do these latent schemas actually correspond to how respondents draw boundaries in the real world? The survey asked respondents to rate various cultural domains (e.g., Music, Food, Clothing, TV Shows) on how effectively they act as markers of distinction (scale of -3 to +3).

We compute the average distinction score for each domain, grouped by the respondent's Good Taste schema.

```{r}
#| label: plot-distinctions
#| fig-width: 10
#| fig-height: 6

library(stringr)

# Select distinction columns
distinction_cols <- grep("Domains_Distinction1_", colnames(analysis_df), value = TRUE)

# Calculate means
distinction_means <- analysis_df %>%
  select(GoodTasteTopic, all_of(distinction_cols)) %>%
  pivot_longer(cols = starts_with("Domains_Distinction1_"), names_to = "Domain", values_to = "Score") %>%
  mutate(
    Domain = str_remove(Domain, "Domains_Distinction1_"),
    Score = as.numeric(Score)
  ) %>%
  filter(!is.na(Score)) %>%
  group_by(GoodTasteTopic, Domain) %>%
  summarize(Mean_Score = mean(Score, na.rm = TRUE), .groups = 'drop')

# Order domains by overall mean rating
domain_order <- distinction_means %>%
  group_by(Domain) %>%
  summarize(Overall = mean(Mean_Score)) %>%
  arrange(Overall) %>%
  pull(Domain)

distinction_means <- distinction_means %>%
  mutate(Domain = factor(Domain, levels = domain_order))

# Plot as a heatmap
p_dist <- ggplot(distinction_means, aes(x = GoodTasteTopic, y = Domain, fill = Mean_Score)) +
  geom_tile(color = "white") +
  scale_fill_gradient2(low = "steelblue", mid = "white", high = "indianred", midpoint = 1.5) +
  theme_minimal(base_size = 14) +
  theme(axis.text.x = element_text(angle = 15, hjust = 1)) +
  labs(
    title = "Average Distinction Rating by Domain and Good Taste Schema",
    x = "Good Taste Schema",
    y = "Cultural Domain",
    fill = "Mean Score"
  )

print(p_dist)
ggsave("Plots/distinction_domains.png", plot = p_dist, width = 10, height = 6)

# Calculate means for Bad Taste
distinction_means_bad <- analysis_df %>%
  select(BadTasteTopic, all_of(distinction_cols)) %>%
  pivot_longer(cols = starts_with("Domains_Distinction1_"), names_to = "Domain", values_to = "Score") %>%
  mutate(
    Domain = str_remove(Domain, "Domains_Distinction1_"),
    Score = as.numeric(Score)
  ) %>%
  filter(!is.na(Score)) %>%
  group_by(BadTasteTopic, Domain) %>%
  summarize(Mean_Score = mean(Score, na.rm = TRUE), .groups = 'drop') %>%
  mutate(Domain = factor(Domain, levels = domain_order))

# Plot Bad Taste Heatmap
p_dist_bad <- ggplot(distinction_means_bad, aes(x = BadTasteTopic, y = Domain, fill = Mean_Score)) +
  geom_tile(color = "white") +
  scale_fill_gradient2(low = "steelblue", mid = "white", high = "indianred", midpoint = 1.5) +
  theme_minimal(base_size = 14) +
  theme(axis.text.x = element_text(angle = 15, hjust = 1)) +
  labs(
    title = "Average Distinction Rating by Domain and Bad Taste Schema",
    x = "Bad Taste Schema",
    y = "Cultural Domain",
    fill = "Mean Score"
  )

print(p_dist_bad)
ggsave("Plots/distinction_domains_bad.png", plot = p_dist_bad, width = 10, height = 6)
```

The heatmap reveals subtle variations in how different schema-holders apply cultural boundaries:
* Across the board, domains like **Music**, **Clothing**, and **Interior Design** are considered strong markers of distinction.
* Domains like **Wrestling** and **Marijuana** are generally not seen as effective markers of distinction. 
* Interestingly, respondents holding the **"Aesthetics/Nuance"** schema for Good Taste draw much harsher, more polarized boundaries—rating traditional high-art domains (like Literature and Paintings) notably higher than those holding the "Mainstream" or "Moral" schemas.
