---
title: "Folk Models of Good and Bad Taste: Master Analysis Pipeline"
format: html
---

::: {.callout-note}
This file consolidates the entire data analysis pipeline (topic modeling, statistical tests, demographic models, and table conversion) into a single document.
:::

# 1. Topic Modeling (Python)

## 1.1 Topic Modeling Pipeline (Definitions Only)
```{python, eval=FALSE}
import pandas as pd
import numpy as np
import json
import os
from bertopic import BERTopic
from sklearn.feature_extraction.text import CountVectorizer, ENGLISH_STOP_WORDS

def run_and_save_bertopic(docs, indices, model_prefix, min_topic_sizes=[5, 10, 15, 20]):
    results = []
    
    # Initialize CountVectorizer with expanded stop words
    domain_stops = ["don", "dont", "t", "didn", "didnt", "doesn", "doesnt", "ve", "ll", "re", "m", "isn", "isnt", "aren", "arent", "wasn", "wasnt", "weren", "werent", "haven", "havent", "hasn", "hasnt", "hadn", "hadnt", "won", "wont", "wouldn", "wouldnt", "can", "cant", "couldn", "couldnt", "shouldn", "shouldnt", "mightn", "mightnt", "mustn", "mustnt", "i've", "don't", "doesn't", "didn't", "isn't", "aren't", "wasn't", "weren't", "haven't", "hasn't", "hadn't", "won't", "wouldn't", "can't", "couldn't", "shouldn't", "mightn't", "mustn't"]
    custom_stop_words = list(ENGLISH_STOP_WORDS.union(domain_stops))
    vectorizer_model = CountVectorizer(stop_words=custom_stop_words)
    
    for size in min_topic_sizes:
        print(f"Running BERTopic for {model_prefix} with min_topic_size={size}...")
        
        # Initialize BERTopic model
        model = BERTopic(
            language="english",
            vectorizer_model=vectorizer_model,
            min_topic_size=size,
            calculate_probabilities=True,
            verbose=True
        )
        
        # Fit model
        topics, probs = model.fit_transform(docs)
        
        # Create output directory
        out_dir = f"{model_prefix}_model_min{size}"
        os.makedirs(out_dir, exist_ok=True)
        
        # Save model
        model.save(out_dir, serialization="safetensors", save_ctfidf=True)
        
        # Save the document-topic probabilities matrix
        probs_df = pd.DataFrame(probs)
        probs_df.insert(0, 'original_index', indices)
        probs_file = os.path.join(out_dir, "document_topic_probabilities.csv")
        probs_df.to_csv(probs_file, index=False)
        print(f"Saved document-topic probabilities to {probs_file}")
        
        # Record number of topics (excluding outlier topic -1)
        topic_info = model.get_topic_info()
        num_topics = len(topic_info[topic_info['Topic'] != -1])
        results.append({"min_topic_size": size, "num_topics": num_topics})
        
        # Save topic info summary
        topic_info.to_csv(os.path.join(out_dir, "topic_info.csv"), index=False)
        
    return results

def process_column(df, col_name, model_prefix):
    series = df[col_name].fillna('').str.strip()
    mask = series != ''
    docs = series[mask].tolist()
    indices = df[mask].index.tolist()
    
    print(f"\n--- Processing {col_name} ---")
    print(f"Loaded {len(docs)} valid documents (removed {len(df) - len(docs)} empty).")
    
    if len(docs) == 0:
        print(f"No documents found for {col_name}, skipping.")
        return []
        
    return run_and_save_bertopic(docs, indices, model_prefix)

def main():
    # Load data
    data_path = "data/FolkTaste_CleanData.csv"
    df = pd.read_csv(data_path)
    
    if "What do you mean" in str(df['GoodTaste_Def'].iloc[0]):
        df = df.drop(0).reset_index(drop=True)
        
    # Restrict to participants who answered YES to Taste_Possibility
    original_len = len(df)
    df = df[df['Taste_Possibility'] == 'YES'].copy()
    print(f"Filtered dataset from {original_len} to {len(df)} participants (Taste_Possibility == 'YES').")
    
    summary = {}
    
    # 1. Good Taste Definitions
    summary["good_taste_def"] = process_column(df, 'GoodTaste_Def', 'good_taste_def')
    
    # 2. Bad Taste Definitions
    summary["bad_taste_def"] = process_column(df, 'BadTaste_Def', 'bad_taste_def')
    
    with open("topic_robustness_summary_def_only.json", "w") as f:
        json.dump(summary, f, indent=4)
        
    print("\nDefinitions models processed. Summary saved to topic_robustness_summary_def_only.json.")

if __name__ == '__main__':
    main()
```

# 2. Chi-Square Associations (Python)

## 2.1 Cross-Tabulations
```{python, eval=FALSE}
import pandas as pd
from scipy.stats import chi2_contingency
import itertools

def get_primary(prob_file):
    df = pd.read_csv(prob_file)
    topic_cols = [c for c in df.columns if c != 'original_index']
    df['primary'] = df[topic_cols].idxmax(axis=1)
    return df[['original_index', 'primary']]

gd = get_primary("good_taste_def_model_min5/document_topic_probabilities.csv").rename(columns={'primary': 'Good_Def'})
bd = get_primary("bad_taste_def_model_min15/document_topic_probabilities.csv").rename(columns={'primary': 'Bad_Def'})

df = gd.merge(bd, on='original_index')

# We will drop outliers for the chi-square analysis
for col in ['Good_Def', 'Bad_Def']:
    df = df[df[col] != '-1']
    df[col] = df[col].apply(lambda x: 'Topic ' + str(x))

domains = ['Good_Def', 'Bad_Def']
for d1, d2 in itertools.combinations(domains, 2):
    print(f"\n======================================")
    print(f"Crosstab: {d1} vs {d2}")
    ct = pd.crosstab(df[d1], df[d2])
    print(ct)
    
    if ct.shape[0] > 1 and ct.shape[1] > 1:
        chi2, p, dof, ex = chi2_contingency(ct)
        print(f"\nChi-square: {chi2:.2f}, p-value: {p:.4f}, df: {dof}")
    else:
        print("Not enough variation for Chi-square.")
```

# 3. Demographic Analysis and Visualizations (R)

## 3.1 Main R Analyses (Wald Tests, Demographics, PCA)
```{r, eval=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(readr)
library(stringr)
library(nnet)
library(car)
library(FactoMineR)
library(factoextra)

dir.create("report/Plots", showWarnings = FALSE)
dir.create("report/Tabs", showWarnings = FALSE)

# 1. Wald Table for Demographics
raw_survey <- read_csv("data/FolkTaste_CleanData.csv", show_col_types = FALSE)
if(grepl("What do you mean", raw_survey$GoodTaste_Def[1])) {
  raw_survey <- raw_survey[-1, ]
}
raw_survey <- raw_survey %>% filter(Taste_Possibility == "YES")
raw_survey$Age <- as.numeric(raw_survey$Age)
raw_survey$EducationLevel_Coded <- as.numeric(raw_survey$EducationLevel_Coded)
raw_survey$Political <- as.numeric(raw_survey$Political)

# ADD python_index globally since it's used multiple times
raw_survey$python_index <- 0:(nrow(raw_survey)-1)

run_multinom <- function(prob_file, name) {
  probs <- read_csv(prob_file, show_col_types = FALSE)
  topic_cols <- setdiff(names(probs), "original_index")
  probs$primary_topic <- apply(probs[, topic_cols], 1, function(row) topic_cols[which.max(row)])
  
  probs_valid <- probs %>% filter(!primary_topic %in% c("-1"))
  
  merged_df <- merge(raw_survey, probs_valid, by.x="python_index", by.y="original_index")
  merged_df$primary_topic <- as.factor(merged_df$primary_topic)
  
  model_data <- merged_df %>% drop_na(Age, Gender, EducationLevel_Coded, Political) %>% filter(Gender %in% c("A man", "A woman"))
  
  if (length(unique(model_data$primary_topic)) > 1) {
    model_data$primary_topic <- relevel(model_data$primary_topic, ref=names(sort(table(model_data$primary_topic), decreasing=TRUE)[1]))
    m <- multinom(primary_topic ~ Age + Gender + EducationLevel_Coded + Political, data=model_data, trace=FALSE)
    w <- Anova(m, type="III")
    
    df <- as.data.frame(w)
    df$Predictor <- rownames(df)
    df$Model <- name
    return(df)
  }
  return(NULL)
}

res1 <- run_multinom("good_taste_def_model_min5/document_topic_probabilities.csv", "Good Taste Def")
res2 <- run_multinom("bad_taste_def_model_min15/document_topic_probabilities.csv", "Bad Taste Def")

all_res <- bind_rows(res1, res2)
all_res <- all_res %>% select(Model, Predictor, `LR Chisq`, Df, `Pr(>Chisq)`)

latex_str <- "\\begin{table}[htpb]\n\\centering\n\\resizebox{\\textwidth}{!}{\n\\begin{tabular}{llrrr}\n\\toprule\n"
latex_str <- paste0(latex_str, "Model & Predictor & Wald $\\chi^2$ & Df & $p$-value \\\\\n\\midrule\n")
for (i in 1:nrow(all_res)) {
  pval <- all_res$`Pr(>Chisq)`[i]
  pval_str <- if(pval < 0.001) "< 0.001" else sprintf("%.4f", pval)
  latex_str <- paste0(latex_str, sprintf("%s & %s & %.2f & %d & %s \\\\\n", 
                                         all_res$Model[i], gsub("_", "\\\\_", all_res$Predictor[i]), all_res$`LR Chisq`[i], all_res$Df[i], pval_str))
}
latex_str <- paste0(latex_str, "\\bottomrule\n\\end{tabular}\n}\n\\caption{Multinomial Logistic Regression Wald Tests for Topic Predictors}\n\\label{tab:wald_models}\n\\end{table}\n")
writeLines(latex_str, "report/Tabs/wald_models.tex")


# 2. Pearson Residual Plots
good_def_probs <- read_csv("good_taste_def_model_min5/document_topic_probabilities.csv", show_col_types = FALSE)
bad_def_probs <- read_csv("bad_taste_def_model_min15/document_topic_probabilities.csv", show_col_types = FALSE)

get_primary <- function(probs, name) {
  topic_cols <- setdiff(names(probs), "original_index")
  probs$primary <- apply(probs[, topic_cols], 1, function(row) topic_cols[which.max(row)])
  res <- probs %>% select(original_index, primary)
  names(res)[2] <- name
  return(res)
}

gd <- get_primary(good_def_probs, "Good_Def")
bd <- get_primary(bad_def_probs, "Bad_Def")

df <- gd %>% inner_join(bd, by="original_index")
df <- df %>%
  filter(Good_Def != "-1", Bad_Def != "-1") %>%
  mutate(
    Good_Def = paste("Topic", Good_Def),
    Bad_Def = paste("Topic", Bad_Def)
  )

tb <- table(df$Good_Def, df$Bad_Def)
if (nrow(tb) > 1 && ncol(tb) > 1) {
  res <- chisq.test(tb)
  residuals_df <- as.data.frame(as.table(res$residuals))
  names(residuals_df) <- c("Var1", "Var2", "Residual")
  
  p <- ggplot(residuals_df, aes(x = Var1, y = Var2, fill = Residual)) +
    geom_tile(color = "white") +
    geom_text(aes(label = round(Residual, 2)), color = "black", size = 4) +
    scale_fill_gradient2(low = "indianred", mid = "white", high = "steelblue", midpoint = 0) +
    scale_x_discrete(position = "top") +
    theme_minimal(base_size = 12) +
    labs(
      title = "Pearson Residuals: Good Def vs Bad Def",
      x = "Good Taste Def",
      y = "Bad Taste Def",
      fill = "Residual"
    )
  ggsave("report/Plots/schema_corr_Good_Def_Bad_Def.png", plot = p, width = 8, height = 6)
}


# 3. PCA of Distinction Domains and Topic ANOVA
dist_cols <- grep("Domains_Distinction1_", names(raw_survey), value = TRUE)
dist_data <- raw_survey %>% select(all_of(dist_cols)) %>% mutate_all(as.numeric)
dist_data_imp <- as.data.frame(lapply(dist_data, function(x) ifelse(is.na(x), mean(x, na.rm = TRUE), x)))
names(dist_data_imp) <- str_remove(names(dist_data_imp), "Domains_Distinction1_")

res.pca <- PCA(dist_data_imp, scale.unit = TRUE, graph = FALSE)
p_pca_var <- fviz_pca_var(res.pca, col.var = "contrib",
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             repel = TRUE, title = "PCA of Cultural Domains Distinction Ratings")
ggsave("report/Plots/pca_domain_variables.png", plot = p_pca_var, width = 8, height = 6)

raw_survey$Dim1 <- res.pca$ind$coord[,1]
raw_survey$Dim2 <- res.pca$ind$coord[,2]
raw_survey$Dim3 <- res.pca$ind$coord[,3]

df_pca <- raw_survey %>%
  left_join(gd, by=c("python_index"="original_index")) %>%
  left_join(bd, by=c("python_index"="original_index"))

df_pca$Good_Def[df_pca$Good_Def == "-1"] <- NA
df_pca$Bad_Def[df_pca$Bad_Def == "-1"] <- NA

run_anova_for_dim <- function(dim_col) {
  results <- list()
  for (model_col in c("Good_Def", "Bad_Def")) {
    test_df <- df_pca %>% select(!!sym(model_col), !!sym(dim_col)) %>% drop_na()
    if (length(unique(test_df[[model_col]])) > 1) {
      formula <- as.formula(paste0("`", dim_col, "` ~ ", model_col))
      aov_res <- aov(formula, data = test_df)
      s <- summary(aov_res)[[1]]
      f_val <- s[["F value"]][1]
      p_val <- s[["Pr(>F)"]][1]
      results[[model_col]] <- data.frame(Model=model_col, F_val=f_val, p_val=p_val)
    }
  }
  res_df <- bind_rows(results)
  res_df$Dimension <- dim_col
  res_df
}

res_dim1 <- run_anova_for_dim("Dim1")
res_dim2 <- run_anova_for_dim("Dim2")
res_dim3 <- run_anova_for_dim("Dim3")

all_res_pca <- bind_rows(res_dim1, res_dim2, res_dim3)
all_res_pca$Format <- sprintf("%.2f (%.3f)", all_res_pca$F_val, all_res_pca$p_val)
all_res_pca$Format <- ifelse(all_res_pca$p_val < 0.001, paste0(all_res_pca$Format, "$^{***}$"), 
                  ifelse(all_res_pca$p_val < 0.01, paste0(all_res_pca$Format, "$^{**}$"),
                  ifelse(all_res_pca$p_val < 0.05, paste0(all_res_pca$Format, "$^{*}$"), all_res_pca$Format)))

wide_res <- all_res_pca %>% select(Dimension, Model, Format) %>%
  pivot_wider(names_from = Model, values_from = Format)

latex_str_pca <- "\\begin{table}[htpb]\n\\centering\n\\begin{tabular}{lcc}\n\\toprule\n"
latex_str_pca <- paste0(latex_str_pca, "Dimension & Good Taste Def & Bad Taste Def \\\\\n\\midrule\n")
for (i in 1:nrow(wide_res)) {
  latex_str_pca <- paste0(latex_str_pca, sprintf("%s & %s & %s \\\\\n", 
        wide_res$Dimension[i], wide_res$Good_Def[i], wide_res$Bad_Def[i]))
}
latex_str_pca <- paste0(latex_str_pca, "\\bottomrule\n\\multicolumn{3}{l}{\\footnotesize $^{*}p<0.05; ^{**}p<0.01; ^{***}p<0.001$} \\\\\n")
latex_str_pca <- paste0(latex_str_pca, "\\end{tabular}\n\\caption{ANOVA Results: Mean Differences in PCA Dimensions of Distinction Ratings by Topic Schema.}\n\\label{tab:anova_pca}\n\\end{table}\n")

writeLines(latex_str_pca, "report/Tabs/anova_pca.tex")

print("R script executed successfully.")
```

## 3.2 ANOVA for Distinction Domains
```{r, eval=FALSE}
library(dplyr)
library(readr)
library(stringr)
library(tidyr)

# 1. Load Data
raw_survey <- read_csv("data/FolkTaste_CleanData.csv", show_col_types = FALSE)
if(grepl("What do you mean", raw_survey$GoodTaste_Def[1])) {
  raw_survey <- raw_survey[-1, ]
}
raw_survey <- raw_survey %>% filter(Taste_Possibility == "YES")
raw_survey$python_index <- 0:(nrow(raw_survey)-1)

# 2. Get Primary Topics
get_primary <- function(path, name) {
  probs <- read_csv(path, show_col_types = FALSE)
  tc <- setdiff(names(probs), "original_index")
  probs[[name]] <- apply(probs[, tc], 1, function(row) tc[which.max(row)])
  probs %>% select(original_index, !!sym(name))
}

gd <- get_primary("good_taste_def_model_min10/document_topic_probabilities.csv", "Good_Def")
bd <- get_primary("bad_taste_def_model_min5/document_topic_probabilities.csv", "Bad_Def")

df <- raw_survey %>%
  left_join(gd, by=c("python_index"="original_index")) %>%
  left_join(bd, by=c("python_index"="original_index"))

# Remove outliers for ANOVA
df$Good_Def[df$Good_Def == "-1"] <- NA
df$Bad_Def[df$Bad_Def == "-1"] <- NA

dist_cols <- grep("Domains_Distinction1_", names(df), value = TRUE)

run_anova_for_model <- function(topic_col) {
  results <- list()
  for (col in dist_cols) {
    domain_name <- str_remove(col, "Domains_Distinction1_")
    
    test_df <- df %>% select(!!sym(topic_col), !!sym(col)) %>% drop_na()
    test_df[[col]] <- as.numeric(test_df[[col]])
    
    if (length(unique(test_df[[topic_col]])) > 1) {
      formula <- as.formula(paste0("`", col, "` ~ ", topic_col))
      aov_res <- aov(formula, data = test_df)
      s <- summary(aov_res)[[1]]
      f_val <- s[["F value"]][1]
      p_val <- s[["Pr(>F)"]][1]
      results[[domain_name]] <- data.frame(Domain=domain_name, F_val=f_val, p_val=p_val)
    }
  }
  res_df <- bind_rows(results)
  res_df$p_adj <- p.adjust(res_df$p_val, method="BH")
  res_df
}

res_gd <- run_anova_for_model("Good_Def")
res_bd <- run_anova_for_model("Bad_Def")

# Format into a single table
combined <- res_gd %>% select(Domain)
format_cell <- function(f, p_adj) {
  sig <- ifelse(p_adj < 0.001, "$^{***}$", ifelse(p_adj < 0.01, "$^{**}$", ifelse(p_adj < 0.05, "$^{*}$", "")))
  sprintf("%.2f%s (%.3f)", f, sig, p_adj)
}

combined$Good_Def <- format_cell(res_gd$F_val, res_gd$p_adj)
combined$Bad_Def <- format_cell(res_bd$F_val, res_bd$p_adj)

dir.create("report/Tabs", showWarnings = FALSE)

# Write to LaTeX
latex_str <- "\\begin{table}[htpb]\n\\centering\n\\resizebox{\\textwidth}{!}{\n\\begin{tabular}{lcc}\n\\toprule\n"
latex_str <- paste0(latex_str, "Domain & Good Taste Def & Bad Taste Def \\\\\n")
latex_str <- paste0(latex_str, "& $F$ ($p_{adj}$) & $F$ ($p_{adj}$) \\\\\n\\midrule\n")

for (i in 1:nrow(combined)) {
  latex_str <- paste0(latex_str, sprintf("%s & %s & %s \\\\\n", 
                                         str_replace_all(combined$Domain[i], "_", "\\\\_"), 
                                         combined$Good_Def[i], combined$Bad_Def[i]))
}

latex_str <- paste0(latex_str, "\\bottomrule\n\\multicolumn{3}{l}{\\footnotesize $^{*}p<0.05; ^{**}p<0.01; ^{***}p<0.001$ (Benjamini-Hochberg FDR corrected)} \\\\\n")
latex_str <- paste0(latex_str, "\\end{tabular}\n}\n\\caption{One-Way ANOVA Results: Mean Differences in Domain Distinction Ratings by Topic Schema. Values are $F$-statistics with FDR-adjusted $p$-values in parentheses.}\n\\label{tab:anova_distinction}\n\\end{table}\n")

writeLines(latex_str, "report/Tabs/anova_distinction.tex")
```

## 3.3 Pearson Residuals and Heatmaps
```{r, eval=FALSE}
library(dplyr)
library(ggplot2)
library(readr)
library(tidyr)
library(stringr)

# --- RE-GENERATE PEARSON RESIDUAL PLOTS ---
raw_survey <- read_csv("data/FolkTaste_CleanData.csv", show_col_types = FALSE)
if(grepl("What do you mean", raw_survey$GoodTaste_Def[1])) raw_survey <- raw_survey[-1, ]
raw_survey <- raw_survey %>% filter(Taste_Possibility == "YES")

gd_probs <- read_csv("good_taste_def_model_min10/document_topic_probabilities.csv", show_col_types = FALSE)
bd_probs <- read_csv("bad_taste_def_model_min5/document_topic_probabilities.csv", show_col_types = FALSE)

get_primary <- function(probs, name) {
  tc <- setdiff(names(probs), "original_index")
  probs$primary <- apply(probs[, tc], 1, function(row) tc[which.max(row)])
  res <- probs %>% select(original_index, primary)
  names(res)[2] <- name
  res
}

gd <- get_primary(gd_probs, "Good_Def")
bd <- get_primary(bd_probs, "Bad_Def")

df <- gd %>% inner_join(bd, by="original_index")

t_g_d <- c("-1"="Outlier", "0"="Similarity/Subjectivity", "1"="Aesthetics", "2"="Style/Quality")
t_b_d <- c("-1"="Outlier", "0"="Dislike/Subjective", "1"="Poor Choices", "2"="Tacky/Loud", "3"="Low-Brow Media", "4"="Immoral", "5"="Poor Manners")

df <- df %>%
  filter(Good_Def != "-1", Bad_Def != "-1") %>%
  mutate(
    Good_Def = t_g_d[as.character(Good_Def)],
    Bad_Def = t_b_d[as.character(Bad_Def)]
  )

combos <- list(c("Good_Def", "Bad_Def"))

for (c in combos) {
  v1 <- c[1]
  v2 <- c[2]
  tb <- table(df[[v1]], df[[v2]])
  if(nrow(tb)>1 && ncol(tb)>1) {
    res <- chisq.test(tb)
    r_df <- as.data.frame(as.table(res$residuals))
    names(r_df) <- c("Var1", "Var2", "Residual")
    
    # Format labels with newlines so they fit horizontally
    r_df$Var1 <- str_replace_all(r_df$Var1, "/", "/\n")
    r_df$Var1 <- str_replace_all(r_df$Var1, " ", "\n")
    
    p <- ggplot(r_df, aes(x = Var1, y = Var2, fill = Residual)) +
      geom_tile(color = "white") +
      geom_text(aes(label = round(Residual, 2)), color = "black", size = 4) +
      scale_fill_gradient2(low = "indianred", mid = "white", high = "steelblue", midpoint = 0) +
      scale_x_discrete(position = "top") +
      theme_minimal(base_size = 12) +
      theme(axis.text.x = element_text(angle = 0, hjust = 0.5, vjust = 0)) +
      labs(
        title = sprintf("Pearson Residuals: %s vs %s", str_replace(v1, "_", " "), str_replace(v2, "_", " ")),
        x = str_replace(v1, "_", " "),
        y = str_replace(v2, "_", " "),
        fill = "Residual"
      )
    ggsave(sprintf("report/Plots/schema_corr_%s_%s.png", v1, v2), plot=p, width=10, height=7)
  }
}

# --- RE-GENERATE HEATMAPS (DEFINITIONS ONLY) ---
df_g_d <- get_primary(gd_probs, "Good_Def")
df_b_d <- get_primary(bd_probs, "Bad_Def")

raw_survey$python_index <- 0:(nrow(raw_survey)-1)
m_df <- raw_survey %>%
  left_join(df_g_d, by=c("python_index"="original_index")) %>%
  left_join(df_b_d, by=c("python_index"="original_index")) %>%
  mutate(
    Good_Def = t_g_d[as.character(Good_Def)],
    Bad_Def = t_b_d[as.character(Bad_Def)]
  )

distinction_cols <- grep("Domains_Distinction1_", names(m_df), value = TRUE)

create_heatmap <- function(data, group_col, title, filename) {
  d_clean <- data %>% filter(!is.na(!!sym(group_col)) & !!sym(group_col) != "Outlier")
  
  dist_means <- d_clean %>%
    select(all_of(group_col), all_of(distinction_cols)) %>%
    pivot_longer(cols = starts_with("Domains_Distinction1_"), names_to = "Domain", values_to = "Score") %>%
    mutate(Domain = str_remove(Domain, "Domains_Distinction1_"), Score = as.numeric(Score)) %>%
    filter(!is.na(Score)) %>%
    group_by(!!sym(group_col), Domain) %>%
    summarize(Mean_Score = mean(Score, na.rm = TRUE), .groups = 'drop')
  
  domain_order <- dist_means %>% group_by(Domain) %>% summarize(Overall = mean(Mean_Score)) %>% arrange(Overall) %>% pull(Domain)
  dist_means <- dist_means %>% mutate(Domain = factor(Domain, levels = domain_order))
  
  # Add newlines to make sure they fit horizontally
  dist_means[[group_col]] <- str_replace_all(dist_means[[group_col]], "/", "/\n")
  dist_means[[group_col]] <- str_replace_all(dist_means[[group_col]], " ", "\n")
  
  p <- ggplot(dist_means, aes(x = !!sym(group_col), y = Domain, fill = Mean_Score)) +
    geom_tile(color = "white") +
    scale_fill_gradient2(low = "steelblue", mid = "white", high = "indianred", midpoint = 1.5) +
    scale_x_discrete(position = "top") +
    theme_minimal(base_size = 14) +
    theme(axis.text.x = element_text(angle = 0, hjust = 0.5, vjust = 0)) +
    labs(title = title, x = "Topic Schema", y = "Cultural Domain", fill = "Mean Score")
  
  ggsave(filename, plot = p, width = 11, height = 7)
}

create_heatmap(m_df, "Good_Def", "Average Distinction Rating by Domain (Good Taste Definitions)", "report/Plots/distinction_domains.png")
create_heatmap(m_df, "Bad_Def", "Average Distinction Rating by Domain (Bad Taste Definitions)", "report/Plots/distinction_domains_bad.png")
```

# 4. Utilities

## 4.1 HTML to LaTeX Table Converter
```{python, eval=FALSE}
from html.parser import HTMLParser
import glob
import os

class TableParser(HTMLParser):
    def __init__(self):
        super().__init__()
        self.in_table = False
        self.in_tr = False
        self.in_th_td = False
        self.current_cell = []
        self.current_row = []
        self.rows = []
        
    def handle_starttag(self, tag, attrs):
        if tag == 'table':
            self.in_table = True
        elif tag == 'tr' and self.in_table:
            self.in_tr = True
            self.current_row = []
        elif tag in ('th', 'td') and self.in_tr:
            self.in_th_td = True
            self.current_cell = []

    def handle_endtag(self, tag):
        if tag == 'table':
            self.in_table = False
        elif tag == 'tr' and self.in_tr:
            self.in_tr = False
            self.rows.append(self.current_row)
        elif tag in ('th', 'td') and self.in_th_td:
            self.in_th_td = False
            cell_text = "".join(self.current_cell).strip().replace('&', '\\&').replace('%', '\\%').replace('_', '\\_')
            self.current_row.append(cell_text)

    def handle_data(self, data):
        if self.in_th_td:
            self.current_cell.append(data)

html_files = glob.glob('report/Tabs/*.html')
for file in html_files:
    try:
        with open(file, 'r', encoding='utf-8') as f:
            content = f.read()
            
        parser = TableParser()
        parser.feed(content)
        
        if not parser.rows:
            continue
            
        tex_file = file.replace('.html', '.tex')
        with open(tex_file, 'w', encoding='utf-8') as f:
            num_cols = len(parser.rows[0])
            col_format = 'l' * num_cols
            f.write('\\begin{table}[htpb]\n')
            f.write('\\centering\n')
            f.write('\\resizebox{\\textwidth}{!}{\n')
            f.write('\\begin{tabular}{' + col_format + '}\n')
            f.write('\\toprule\n')
            
            for i, row in enumerate(parser.rows):
                f.write(' & '.join(row) + ' \\\\\n')
                if i == 0:
                    f.write('\\midrule\n')
                    
            f.write('\\bottomrule\n')
            f.write('\\end{tabular}\n')
            f.write('}\n')
            # generate caption from filename
            caption = os.path.basename(file).replace('_', ' ').replace('.html', '').title()
            f.write(f'\\caption{{{caption}}}\n')
            # generate label
            label = os.path.basename(file).replace('.html', '')
            f.write(f'\\label{{tab:{label}}}\n')
            f.write('\\end{table}\n')
            
        print(f"Converted {file} to {tex_file}")
    except Exception as e:
        print(f"Failed to convert {file}: {e}")
```
